SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-27 docs/questioning.tex
updated Figure 2
more on figure 2

In this section we provide a step-by-step exploitation model to
understand the process of carrying out application attacks based on
executable source code injection vulnerabilities.
Figure~\ref{fig:attacks} presents the steps of different application
attacks. For the most part, the steps are common in all attacks. This
is because they are based on similar attack vectors as we mentioned in
the previous section. Most importantly,
Figure~\ref{fig:attacks} also illustrates in which step
the defenses detect corresponding attacks ({\sc todo}).

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.55]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities ({\sc draft}).}
\end{figure*}

@@

\section{Web Application Attacks Defenses}
\label{sec:defs}

>>>>

In this section we provide a step-by-step exploitation model to
understand the process of carrying out application attacks based on
executable source code injection vulnerabilities.
Figure~\ref{fig:attacks} presents the steps of different application
attacks. For every arrow there is a
corresponding tuple that includes the step number for
every attack. For the most part, the steps are common in all attacks. This
is because they are based on similar attack vectors as we mentioned in
the previous section. Most importantly,
Figure~\ref{fig:attacks} also illustrates in which step
the defenses detect corresponding attacks ({\sc todo}).

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.55]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. {\sc p-xss} stands for a persistent {\sc xss}
attack and {\sc n-xss} stands for a non persistent {\sc xss}
attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references: ({\sc draft}).}
\end{figure*}

@@

\section{Approaches}
\label{sec:defs}
